### 2020-11-10 paper/draft1.tex
using m_delta

@@

In [elf paper] Theorem 6, they show that ELF is strictly truthful. In Theorem 8, they also show it is accurate. Specifically, that for an accuracy gap of $\epsilon$, that ELF chooses the most accurate forecaster with probability $ \geq 1 - \delta$ if
\[ m \geq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
For a fixed forecaster accuracy gap and mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$. However, this lower bound is not tight, and can be improved.

@@

Applying Theorem \ref{bernstein}, we have
\begin{align*}
    P\left(\left| F_i - \E[F_i]\right| < \frac{m \epsilon}{2(n - 1)} \right) 
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{2m}{n} + \frac{m \epsilon}{6(n - 1)}\right)}} \\
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{m}{n-1}(2 + \frac{\epsilon}{6}) \right)}} \\
    &= 2 \: e^{\frac{-\frac{m \epsilon^2}{2(n - 1)} }{(2 + \frac{\epsilon}{6})}} \\
    &< 2 \: e^{-\frac{m \epsilon^2}{6(n - 1)} }  \numberthis \label{elf_bernstein} 
\end{align*}
And similarly for $F_j$. Putting both of those cases together, we have by the union bound
\begin{align*}
  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon/62}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
  &\leq P\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) + P\left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \\
  &\leq 4 \: e^{-\frac{m \epsilon^2}{6(n - 1)} }
\end{align*}
Using the union bound over all $j$, we have
\begin{align*}
  P\left(M_l(y_1, ..., y_n, x) = i\right)
  &= 1 - \sum_{j\neq i} P\left(M_l(y_1, ..., y_n, x) = j\right) \\
  &\geq 1 - \sum_{j\neq i} P\left(F_j \geq F_i\right) \\
  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{6(n - 1)}} 
\end{align*}
\hfill\QED

Assigning this probability to $1 - \delta$, we can see that for a fixed $n, \epsilon$, ELF chooses the correct forecaster with probability at least $1 - \delta$ if
\[m \geq \frac{6(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]

@@

(section 4.3, proposition 5).  For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random. In the first case, the expected number of other forecasters who also score 1 is $\sum_{i' \neq i} \E_{x \sim \theta} f_{i'} = \sum_{i' \neq i} (a_{i'} + \theta^2 - \theta) = (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}$. Then, the probability that forecaster $i$ is chosen is 
\[
  P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
\]
In the other case, the probability $i$ wins is just 
\[
  \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
\]

@@

multiple events: (section 5.3, theorem 8)
Let $a_i \geq a_j + \epsilon$ for all $j\neq i$. Like in theorem 8, we first bound the expected number of events won that $i$ exceeds $j$ by. 
\begin{align*}
  \E \left( \sum_{k=1}^m f_{i, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
  &= \left( \sum_{k=1}^m \E f_{i, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
  &= \sum_{k=1}^m \left(\E (f_{i, k}) - \E (f_{j, k})\right)\\
  &= \sum_{k=1}^m \left((a_i + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
  &= \sum_{k=1}^m \left(a_i - a_j\right)\\
  &\geq \sum_{k=1}^m \epsilon\\
  &=m \epsilon
\end{align*}
If $F_j \geq F_i$, then either $\E(F_i) - F_i \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$. By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$. Using the union bound, the probability that either of those events occurs is twice this, or $4 e^{\frac{- m \epsilon^2}{2}}$.

Using the union bound again over all $j \neq i$, we have 
\[
1 - \delta = P(M(y_1, ..., y_n, x) = i) = 1 - \sum_{j \neq i} P(F_j \geq F_i) = 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
\]
Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when 
\[ m \geq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]

>>>>

define $m_\delta$

@@

In [elf paper] Theorem 6, they show that ELF is strictly truthful. In Theorem 8, they also show it is accurate. Specifically, that for an accuracy gap of $\epsilon$, ELF has
\[ m_\delta \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
For a fixed forecaster accuracy gap and desired mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$. However, this upper bound is not tight, and can be lowered significantly.

@@

Applying Theorem \ref{bernstein}, we have
\begin{align*}
    P\left(\left| F_i - \E[F_i]\right| < \frac{m \epsilon}{2(n - 1)} \right) 
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{2m}{n} + \frac{m \epsilon}{6(n - 1)}\right)}} \\
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{m}{n-1}(2 + \frac{\epsilon}{6}) \right)}} \\
    &= 2 \: e^{\frac{-\frac{m \epsilon^2}{2(n - 1)} }{(2 + \frac{\epsilon}{6})}} \\
    &< 2 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }  \numberthis \label{elf_bernstein} 
\end{align*}
And similarly for $F_j$. Putting both of those cases together, we have by the union bound
\begin{align*}
  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
  &\leq P\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) + P\left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \\
  &\leq 4 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }
\end{align*}
Using the union bound over all $j$, we have
\begin{align*}
  P\left(M_l(y_1, ..., y_n, x) = i\right)
  &= 1 - \sum_{j\neq i} P\left(M_l(y_1, ..., y_n, x) = j\right) \\
  &\geq 1 - \sum_{j\neq i} P\left(F_j \geq F_i\right) \\
  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{5(n - 1)}} 
\end{align*}
\hfill\QED

Assigning this probability to $1 - \delta$, we see that for a fixed $n, \epsilon$, ELF will choose the correct forecaster with probability at least $1 - \delta$ if $m$ is large enough for the above inequality to hold. Solving it for $m$, we get the minimum such satisfying value
\[m_\delta \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]

@@

\subsection{Truthfulness for a single event}
(section 4.3, proposition 5).  For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random. In the first case, the expected number of other forecasters who also score 1 is $\sum_{i' \neq i} \E_{x \sim \theta} f_{i'} = \sum_{i' \neq i} (a_{i'} + \theta^2 - \theta) = (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}$. Then, the probability that forecaster $i$ is chosen is 
\[
  P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
\]
In the other case, the probability $i$ wins is just 
\[
  \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
\]

@@

\subsection{Truthfulness for multiple events}
multiple events: (section 5.3, theorem 8)
Let $a_i \geq a_j + \epsilon$ for all $j\neq i$. Like in theorem 8, we first bound the expected number of events won that $i$ exceeds $j$ by. 
\begin{align*}
  \E \left( \sum_{k=1}^m f_{i, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
  &= \left( \sum_{k=1}^m \E f_{i, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
  &= \sum_{k=1}^m \left(\E (f_{i, k}) - \E (f_{j, k})\right)\\
  &= \sum_{k=1}^m \left((a_i + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
  &= \sum_{k=1}^m \left(a_i - a_j\right)\\
  &\geq \sum_{k=1}^m \epsilon\\
  &=m \epsilon
\end{align*}
If $F_j \geq F_i$, then either $\E(F_i) - F_i \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$. By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$. Using the union bound, the probability that either of those events occurs is twice this, or $4 e^{\frac{- m \epsilon^2}{2}}$.

Using the union bound again over all $j \neq i$, we have 
\[
1 - \delta = P(M(y_1, ..., y_n, x) = i) = 1 - \sum_{j \neq i} P(F_j \geq F_i) = 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
\]
Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when $m$ is large enough to satisfy the inequality. Solving for $m$ gives us the minimum such value, which is an upper bound of $m_\delta$ for SHELF.
\[ m_\delta \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
